Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-06-28 Paper/main.tex
maint.tex modified
new pendings

\begin{figure}[H]
    \centering
    \includegraphics{covariates_categorical.png}
    \caption{Covariate distribution for Pilot and Historical Data: continuous variables}
    \label{covariates_categorical}
\end{figure}

\begin{figure}[H]
\caption{Covariate distribution in Historical and Pilot data}
\label{covariate_distribution}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Continuous variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_continous.png}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Categorical variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_categorical.png}
        \end{subfigure}
    \end{center}
\end{figure}

@@

\begin{figure}[H]
    \caption{Conciliation over time}
    \label{Figure_dynamicsConciliation}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{con_overtime.pdf}
     \end{subfigure}
        \begin{subfigure}{0.49\textwidth}    
         \centering
        \includegraphics[width=1\textwidth]{beta_monthsafter.pdf}
     \end{subfigure}
        \end{center}
        {\footnotesize \textit{Notes: } Conciliation over time in HD database and pilot database. Figure on the left shows the effect of conciliation on treated against control for different months after initial sue.}
        {\footnotesize \textit{Do file: } \texttt{con\_overtime.do , beta\_monthsafter.do}}
\end{figure}

>>>>

\begin{figure}[H]
\caption{Covariate distribution in Historical and Pilot data}
\label{covariate_distribution}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Continuous variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_continuous.png}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Categorical variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_categorical.png}
        \end{subfigure}
    \end{center}
    {\footnotesize \textit{Notes: } Covariate distributions for historical -used to calibrate our calculator- and pilot data. All continuous variables are plotted in logs. Color guide is the same for both variable types.}
    {\footnotesize \textit{Script: } \texttt{covariate\_plots.R}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Conciliation over time}
    \label{Figure_dynamicsConciliation}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{con_overtime.pdf}
     \end{subfigure}
        \begin{subfigure}{0.49\textwidth}    
         \centering
        \includegraphics[width=1\textwidth]{beta_monthsafter.pdf}
     \end{subfigure}
        \end{center}
        {\footnotesize \textit{Notes: } Conciliation over time in HD database and pilot database. Figure on the right shows the effect of conciliation on treated against control for different months after initial sue.}
        {\footnotesize \textit{Do file: } \texttt{con\_overtime.do , beta\_monthsafter.do}}
\end{figure}

\begin{figure}[H]
    \caption{ }
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{}
     \end{subfigure}

        \begin{subfigure}{0.49\textwidth}    
         \centering
        \includegraphics[width=1\textwidth]{}
     \end{subfigure}

     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{}
     \end{subfigure}

        \end{center}
        {\footnotesize \textit{Notes: } }
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}
